Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Cont_Syn.tex
new inverted pendulum

We implemented our algorithm in a Python script which interfaces between Matlab
and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
The interface parses the output from Matlab and encodes the matrices \texttt{F,
G, H, K} and the error bounds in Daisy's input format.
\eva{Can we say something about parallelization?}

>>>>

We implemented our algorithm in a Python script which interfaces between Matlab
and Daisy and which implements the high-level structure from~\autoref{lst:alg}.
The interface parses the output from Matlab and encodes the matrices \texttt{F,
G, H, K} and the error bounds in Daisy's input format.

We run the precision tuning for control actions (line 12) and hyperplanes (line 13) in
parallel, because the analysis of a single region or hyperplane is completely independent from
the others. 
We currently first perform precision tuning for control actions and then for
hyperplanes. These two steps could be run concurrently as well, though the
impact is likely going to be minimal because the number of hyperplanes is
usually an order of magnitude greater than the number of regions.

% A relatively simple improvement to the current parallelization could be to run precision tuning for hyperplanes and active functions together, without waiting for the latter to terminate. Nevertheless, we suspect a minimal impact on performance, because usually the number of hyperplanes is an order of magnitude greater than regions. Thus, this is the main bottleneck of the algorithm. 
%\eva{Can we say something about parallelization?}
